\begin{abstract}
	Terrain modelling and representation is an elaborated topic in computer graphics and visualization. This report highlights some of the state-of-the-art techniques for large scale modelling of terrains, as well as modelling procedurally generation of content. We take a closer look on feature based modeling approach, where iconic landmarks, such as rivers or hills, can be combined with base terrain features to produce arbitrary, but realistic looking terrains. A large part in terrain generation is the creation of drainage networks and the influence of fluids to the terrain. We examine a procedure, that generates a functioning river network and create a terrain around it. Lastly the influence of water on terrain is a big research field. Here we look deeper into algorithms, that simulate the erosion of terrain due to fluid streams, accounting for both sediment and dissolve of soil material. 
	Also particle based calculation models are a very important topic in this field. Most of the utilized algorithms are purely physics-based have just been simplified to yield better results and/or to reduce it's computational demands. Due to some of those algorithms being quite complex, they go far beyond the scope of this report. Therefore it is our goal to present an overview of available techniques, rather than providing an exact and complete summary of the underlying publications.

	
	\begin{classification} % according to http://www.acm.org/about/class/2012
		\CCScat{Computing methodologies}{Computer graphics}{Rendering}
	\end{classification}
	
\end{abstract}
